Visualization

### 2023-01-11 Code/simulation.Rmd
Clean Folders

@@

>>>>

```{r ma = .1, n = 125}
n <- 125
blksize <- 5
theta <- .1
target <- c(0, 1, theta / (1 + theta^2))
set.seed(1234)
sim_.1_125 <- replicate(nrep, do1rep(n, theta, mystat, blksize))
mychk(sim_.1_125, target)
```

```{r ma = .1, n = 1000}
n <- 1000
blksize <- 10
theta <- .1
target <- c(0, 1, theta / (1 + theta^2))
set.seed(2345)
sim_.1_1k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
mychk(sim_.1_1k, target)
```

```{r ma = .1, n = 3375}
n <- 3375
blksize <- 15
theta <- .1
target <- c(0, 1, theta / (1 + theta^2))
set.seed(3456)
sim_.1_3375 <- replicate(nrep, do1rep(n, theta, mystat, blksize))
mychk(sim_.1_3375, target)
```

@@

```{r ma = .5, n = 3375}
n <- 3375
blksize <- 15
theta <- .5
target <- c(0, 1, theta / (1 + theta^2))
set.seed(3456)
sim_.5_3375 <- replicate(nrep, do1rep(n, theta, mystat, blksize))
mychk(sim_.5_3375, target)
```

```{r ma = .5, n = 8000}
n <- 8000
blksize <- 20
theta <- .5
target <- c(0, 1, theta / (1 + theta^2))
set.seed(4567)
sim_.5_8k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
mychk(sim_.5_8k, target)
```

```{r}
write.csv(sim_.1_125,"../Data/Raw/sim_.1_125.csv", row.names = FALSE)
write.csv(sim_.1_1k,"../Data/Raw/sim_.1_1k.csv", row.names = FALSE)
write.csv(sim_.3_125,"../Data/Raw/sim_.3_125.csv", row.names = FALSE)
write.csv(sim_.3_1k,"../Data/Raw/sim_.3_1k.csv", row.names = FALSE)
write.csv(sim_.3_3375,"../Data/Raw/sim_.3_3375.csv", row.names = FALSE)
write.csv(sim_.3_8k,"../Data/Raw/sim_.3_8k.csv", row.names = FALSE)
```
